### 2024-05-21 thesis/input_files/analysis.tex
thesis update

\section{Point forecasting}
This section carries out a comparative study between the state of the art methods for point forecasting, introduced in \ref{ch:point}.
As use case, we will consider the task of predicting the electric load from the GEFCom 2014 dataset.
In such setting we considered the following regressors
\begin{itemize}
    \item Day
    \item Hour
    \item Month
    \item Day of the week
    \item Is holiday
    \item Weather temperature
\end{itemize}
Methods will be compared by means of the RMSE, MAE and MAPE scores, see section \ref{metrics}.
\subsection{Multiple linear regression}
To get started, standard multiple linear regression has been applied, see fig \ref{fig:mlr_price} for a visualisation. 
\begin{figure}
    \includegraphics[width=\textwidth]{images/mlr_price.png}
    \caption{Multiple linear regression prediction}
    \label{fig:mlr_price}
\end{figure}

@@

% \begin{figure}[!h]
%     \includegraphics[width=\textwidth]{images/prophet_price2.2.png}
%     \caption{Prices trend}
%     \label{fig:prophet_price2.2}
% \end{figure}
Prophet alongside with the right features is a good model in the context of electricity price forecasting, it is capcable of catching the trend, the peak and the lows.

@@

\subsection{Long short term memory}
We used the torch library in order to code our LSTM regressor.
Various hyperparameters combinations were tried during the tuning phase. The final architecture we set on follows
\begin{itemize}
    \item hidden\_size= 64
    \item num\_layers= 2
    \item output\_size= 1
    \item num\_epochs= 30
    \item learning\_rate= 0.001
    \item batch\_size= 32
    \item window\_size= 24
\end{itemize}
LSTM forecast is reported in figure \ref{fig:lstm_price}, it achieves a RMSE of 9.1782
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/lstm_price.png}
    \caption{Long short term memory prediction}
    \label{fig:lstm_price}
\end{figure}

\subsection{Kernel ridge regression}
Subsequently, kernel ridge regression was considered. The kernel considered is the radial basis gaussian function.
Cross validation was carried jointly over the rbf kernel bandwith and the regularization constant.
The RMSE achieved is 9.86, figure \ref{fig:krnridge_price} reports the prediction.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/krnridge_price.png}
    \caption{Kernel ridge prediction}
    \label{fig:krnridge_price}
\end{figure}
We can observe that, kernel ridge regression models accurately the electricity time series.

@@

\subsection{Results}
This section reports the table comparing the considered methods scores 
% in the context of electricity load forecasting.

@@

The MAE scores are contained in table \ref{tab:point_MAE}. Similarly to above, we can conclude that kernel methods stand out for achieving also the lowest MAE score.
\begin{table}[!ht]
    \caption{Mean absolute errors}
    \label{tab:point_MAE}
    \begin{adjustbox}{width=\textwidth}
        \begin{tabular}{lrrrrrrrrrrrrrrr}
            \toprule
             Method/MAE & Task 1 & Task 2 & Task 3 & Task 4 & Task 5 & Task 6 & Task 7 & Task 8 & Task 9 & Task 10 & Task 11 & Task 12 & Task 13 & Task 14 & Task 15 \\
            \midrule
            MLR & 27.7219 & 24.3823 & 65.4016 & 52.3873 & 34.8465 & 31.2663 & 35.9420 & 34.7316 & 37.0273 & 54.7075 & 48.9327 & 26.1975 & 31.8720 & 29.2306 & 28.3428 \\
            TBATS & 10.5408 & 23.8417 & 91.3153 & 74.5734 & 40.3258 & 26.0092 & 14.2141 & 24.7818 & 62.0452 & 86.7125 & 72.6912 & 28.4235 & 11.1184 & 21.1038 & 31.8555 \\
            Prophet & 8.6139 & 11.4307 & 28.3509 & 46.4480 & 15.6290 & 14.1278 & 10.1574 & 11.2360 & 14.0072 & 18.9565 & 27.1142 & 16.9678 & 14.6615 & 16.1750 & 18.3043 \\
            KNN & 9.4003 & 9.1126 & 19.6213 & 14.4906 & 10.6461 & \textbf{9.4354} & 8.7441 & 10.0065 & 12.4714 & 11.2006 & 20.3087 & 12.5416 & 9.2558 & 8.5937 & 10.5451 \\
            SVR & 20.2443 & 21.2526 & 69.3704 & 57.1107 & 34.3651 & 27.5875 & 27.4651 & 29.4204 & 43.7009 & 64.3522 & 55.4307 & 25.1080 & 24.0294 & 24.4049 & 26.5869 \\
            LSTM & 7.5217 & 9.4767 & \textbf{17.9851} & \textbf{13.2158} & 11.8118 & 9.8607 & \textbf{8.0561} & 10.8480 & 15.1008 & 13.8108 & 25.9906 & 13.3588 & 8.1526 & 9.8000 & 14.3186 \\
            KrnRidge & 7.5965 & 9.2130 & 28.2484 & 24.2366 & \textbf{10.0589} & 10.7758 & 9.5788 & 11.2166 & 12.3427 & 12.3306 & 20.0213 & 10.8434 & 7.1625 & \textbf{7.9710} & 10.0767 \\
            KrnSVR & \textbf{6.9581} & \textbf{8.6989} & 18.7739 & 15.1398 & 10.1395 & 9.5927 & 8.5731 & \textbf{9.0033} & \textbf{11.0618} & \textbf{8.5486} & \textbf{19.7383} & \textbf{10.5545} & \textbf{7.0395} & 8.1926 & \textbf{9.8125} \\
            \bottomrule
            \end{tabular}            
    \end{adjustbox}            
\end{table}

Finally table \ref{tab:point_MAPE} reports the MAPE score for each method. What can be concluded is that kernel regressors are also the best in terms of MAPE score; with KrnSVR being the top one.
\begin{table}[!ht]
    \caption{Mean absolute percentage errors}
    \label{tab:point_MAPE}
    \begin{adjustbox}{width=\textwidth}
        \begin{tabular}{lrrrrrrrrrrrrrrr}
            \toprule
             Method/MAPE & Task 1 & Task 2 & Task 3 & Task 4 & Task 5 & Task 6 & Task 7 & Task 8 & Task 9 & Task 10 & Task 11 & Task 12 & Task 13 & Task 14 & Task 15 \\
            \midrule
            MLR & 0.2470 & 0.1935 & 0.3030 & 0.2601 & 0.2474 & 0.2667 & 0.3498 & 0.3058 & 0.1954 & 0.2432 & 0.4234 & 0.2114 & 0.2926 & 0.2502 & 0.2145 \\
            TBATS & 0.0833 & 0.1650 & 0.4285 & 0.3731 & 0.2482 & 0.1849 & 0.1234 & 0.1634 & 0.3181 & 0.4021 & 0.4880 & 0.1761 & 0.0905 & 0.1555 & 0.2058 \\
            Prophet & 0.0737 & 0.0854 & 0.1324 & 0.2453 & 0.1134 & 0.1169 & 0.0938 & 0.0912 & 0.0880 & 0.0992 & 0.3757 & 0.1389 & 0.1343 & 0.1356 & 0.1370 \\
            KNN & 0.0778 & 0.0682 & 0.0924 & 0.0761 & 0.0751 & 0.0740 & 0.0784 & 0.0744 & 0.0725 & 0.0555 & \textbf{0.3115} & 0.0888 & 0.0816 & 0.0699 & 0.0765 \\
            SVR & 0.1808 & 0.1640 & 0.3211 & 0.2829 & 0.2317 & 0.2260 & 0.2676 & 0.2451 & 0.2215 & 0.2867 & 0.4354 & 0.1870 & 0.2216 & 0.2044 & 0.1933 \\
            LSTM & 0.0642 & 0.0706 & 0.0896 & \textbf{0.0722} & 0.0798 & 0.0772 & \textbf{0.0710} & 0.0854 & 0.0909 & 0.0741 & 0.3578 & 0.0976 & 0.0719 & 0.0778 & 0.1037 \\
            KrnRidge & 0.0625 & 0.0685 & 0.1281 & 0.1207 & 0.0718 & 0.0797 & 0.0812 & 0.0760 & 0.0696 & 0.0587 & 0.3127 & 0.0779 & \textbf{0.0591} & \textbf{0.0637} & 0.0722 \\
            KrnSVR & \textbf{0.0568} & \textbf{0.0642} & \textbf{0.0892} & 0.0788 & \textbf{0.0714} & \textbf{0.0724} & 0.0740 & \textbf{0.0665} & \textbf{0.0629} & \textbf{0.0428} & 0.3122 & \textbf{0.0781} & 0.0607 & 0.0646 & \textbf{0.0713} \\
            \bottomrule
            \end{tabular}            
    \end{adjustbox}
\end{table}

\section{Probabilistic forecasting}
We continue our experimental analysis by considering the probabilistic framework. The goal of this section is comparing between different quantile regressors and study the choiche of the kernel function.

% quantile regressors
\subsection{Quantile regressors comparison}
Using the load data from \href{https://www.energy-charts.info/index.html?l=en&c=DE}{energy charts} for Germany and Switzerland, we proceeded to compare between quantile regression algorithms. In this study, we trained our models on the entire 2021 data and then we tested them and measured their score on the 2022 data.
Notice, for kernel quantile regression (KQR), the kernel of choice in this setting is the absolute Laplacian. Finally notice, the loss function utilized in this section is the normalized pinball loss. 
% normalized by the magnitude of the average load of each country.
Here, we built two models. In the first, the national load is forecasted by taking as predictor the following variables
\begin{itemize}
    \item Weather temperature
    \item Wind speed
\end{itemize}
Results for Germany are reported in table \ref{tab:energy_chart_de} and figure \ref{fig:DE_load_CI} while results for Switzerland can be found in table \ref{tab:energy_chart_ch} and figure \ref{fig:CH_load_CI}.

@@

    \begin{figure}[!ht]
        \makebox[\linewidth]{\includegraphics[width = 1.5\textwidth]{images/DE_load_CI.png}}
        \caption[Probabilistic forecast for load in Germany]{Load 90\% confidence interval for Germany Energy charts data using KQR Laplacian: \small \textmd{Electric load probabilistic forecast Germany 2022. The black line is the observed path for the load. The 90\% confidence interval bands are plotted in green. Lower and upper red lines denote the 95\% and 5\% quantile forecast respectively.}}
        \label{fig:DE_load_CI}
    \end{figure}

    \begin{figure}[!ht]
        \makebox[\linewidth]{\includegraphics[width = 1.5\textwidth]{images/CH_load_CI.png}}
        \caption[Probabilistic forecast for load in Switzerland]{Load 90\% confidence interval for Switzerland Energy charts data using KQR Laplacian: \small \textmd{Electric load probabilistic forecast for Switzerland 2022. The black line is the observed path for the load. The 90\% confidence interval bands are plotted in green. Lower and upper red lines denote the 95\% and 5\% quantile forecast respectively.}}
        \label{fig:CH_load_CI}
    \end{figure}

Next, we extended the models to take into account the impact of two additional categorical variables
\begin{itemize}
    \item Is holiday: a binary variable for holidays where holiday$=1$ and working day$=0$
    \item Day of week: an ordinal categorical variable corresponding to the day of the week , e.i.\ Monday$=0$,$\dots$, Sunday$=6$
\end{itemize}
Table \ref{tab:energy_chart_de_additional_predictors} reports the model score on the German data while table \ref{tab:energy_chart_ch_additional_predictors} is the one corresponding to the Suisse data.

\begin{table}[!ht]
    \centering
    \caption{PF pinball loss for load in Germany (2022) model\_2}
    \label{tab:energy_chart_de_additional_predictors}
    \begin{tabular}{lrrrr}
    \toprule
    Quantile & LQR & GBMQR & QF & KQR \\
    \midrule
    0.1 & 0.04522 & 0.02580 & 0.02796 & \textbf{0.02491} \\
    0.2 & 0.08048 & 0.04326 & 0.04625 & \textbf{0.04209} \\
    0.3 & 0.10677 & 0.05570 & 0.05706 & \textbf{0.05424} \\
    0.4 & 0.12610 & 0.06182 & 0.06346 & \textbf{0.06071}\\
    0.5 & 0.13767 & 0.06214 & 0.06544 & \textbf{0.06150} \\
    0.6 & 0.14077 & 0.05752 & 0.06001 & \textbf{0.05726} \\
    0.7 & 0.13409 & 0.04893 & 0.05122 & \textbf{0.04869} \\
    0.8 & 0.11628 & 0.03687 & 0.03822 & \textbf{0.03665} \\
    0.9 & 0.08204 & 0.02114 & 0.02324 & \textbf{0.02108} \\
    \midrule
    CRPS & 0.10771 & 0.04591 & 0.04810 & \textbf{0.04524} \\
    \bottomrule
    \end{tabular}
    \end{table}

@@

% now comment tables
What can be concluded from this first study is that kernel quantile regression equipped with the absolute laplacian kernel outperformed almost always its contenders.

% kernel comparison
\subsection{Kernel function choice}
This section analyzes which kernel function best fits to the characteristics of the load data.
The kernel functions considered are: Gaussian RBF, absolute Laplacian, Matern 1.5, Matern 2.5,Linear, Periodic, Polynomial, Sigmoid, and Cosine. 
Details concerning the hyperparameter selection for the different kernels can be found in \href{https://scikit-learn.org/stable/modules/classes.html#module-sklearn.metrics.pairwise}{sklearn.metrics.pairwise} and \href{https://scikit-learn.org/stable/modules/classes.html#module-sklearn.gaussian_process}{sklearn.gaussian\_process}.
The pool of data for this study has been create by combining \href{https://zenodo.org/records/7907883}{SECURES-Met} data (predictors) \cite{Formayer2023} and the load data from \href{https://www.energy-charts.info/index.html?l=en&c=DE}{energy charts}.
SECURES-Met data consists of historical data up to the end of $2020$ while from 2021 onward, the data consists of forecasts modeled by the the European Centre for Medium-Range Weather Forecasts (ECMWF).
Therefore, in this experimental study, we used the whole data of $2020$ as the training set and then tested our kernels on the $2021$ data.
Note that there are two kinds of predictions for data from $2021$ onward, one for each of the emission scenarios RCP$4.5$ and RCP$8.5$. In this study, we considered the more conservative RCP$4.5$ scenario data.

The predictors making up the dataset follow:
\begin{itemize}
    \item Direct irradiation: direct normal irradiation
    \item Global radiation: mean global radiation
    \item Hydro reservoir: daily mean power from reservoir plants in MW
    \item Hydro river: daily mean power from run of river plants in MW
    \item Temperature: air temperature
    \item Wind potential: potential wind power production
\end{itemize}
Table \ref{tab:secures_met_de} shows results for Germany, table \ref{tab:secures_met_ch} is the one for Switzerland and table corresponds to Austria \ref{tab:secures_met_at}.

@@

\begin{table}[!ht]
    \centering
\caption{Pinball loss kernel comparison for load in German (2021)}
\label{tab:secures_met_de}
\begin{adjustbox}{width=\textwidth}
    \begin{tabular}{llllllllll}
\toprule
Quantile & Gaussian RBF & Laplacian & Matern 1.5 & Matern 2.5 & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
\midrule
0.1 & 0.028057 & \textbf{0.027483} & 0.028236 & 0.028257 & 0.028261 & 0.028277 & 0.028276 & 0.028146 & 0.028004 \\
0.2 & 0.047118 & \textbf{0.046051} & 0.047531 & 0.047544 & 0.047569 & 0.047595 & 0.047596 & 0.047353 & 0.047025 \\
0.3 & 0.060366 & \textbf{0.058739} & 0.060892 & 0.060940 & 0.060962 & 0.060988 & 0.060984 & 0.060654 & 0.060209 \\
0.4 & 0.068344 & \textbf{0.066347} & 0.068952 & 0.069022 & 0.069054 & 0.069104 & 0.069101 & 0.068634 & 0.068202 \\
0.5 & 0.071450 & \textbf{0.069118} & 0.072188 & 0.072250 & 0.072285 & 0.072331 & 0.072330 & 0.071807 & 0.071359 \\
0.6 & 0.068821 & \textbf{0.067098} & 0.069454 & 0.069526 & 0.069571 & 0.069615 & 0.069613 & 0.069157 & 0.068780 \\
0.7 & 0.061150 & \textbf{0.059972} & 0.061382 & 0.061410 & 0.061427 & 0.061442 & 0.061442 & 0.061281 & 0.060990 \\
0.8 & 0.047147 & \textbf{0.046457} & 0.047325 & 0.047331 & 0.047340 & 0.047348 & 0.047349 & 0.047247 & 0.047056 \\
0.9 & 0.026646 & 0.026343 & 0.026749 & 0.026757 & 0.026763 & 0.026772 & 0.026772 & \textbf{0.026282} & 0.026628 \\ 
\midrule
CRPS & 0.053233 & \textbf{0.051956} & 0.053634 & 0.053671 & 0.053693 & 0.053719 & 0.053718 & 0.053395 & 0.053139 \\
\bottomrule
\end{tabular}
\end{adjustbox}
\end{table}

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\linewidth]{images/price_task_6_gaussian_rbf.png}
    \caption[[Prediction price track task 6, Gaussian RBF kernel]]{Price 90\% confidence interval task 6: \small \textmd{Electricity price probabilistic forecast for the $13^{\text{th}}$ July $2013$. The black line is the observed path for the price. The $90\%$ confidence interval bands are plotted in green. Lower and upper red lines denote the $95\%$ and $5\%$ quantile forecast respectively.}}
    % \Description{}
    \label{fig:price_task_6_gaussian_rbf}
\end{figure}

>>>>

\section{Point forecasting}
This section carries out a comparative study between the state of the art methods for point forecasting, introduced in \ref{ch:point}.
As use case, we will consider the task of predicting the electric load from the GEFCom 2014 dataset.
In such setting we considered the following regressors
\begin{itemize}
    \item Day
    \item Hour
    \item Month
    \item Day of the week
    \item Is holiday: a binary variable for holidays, where holiday$=1$ and working day$=0$
    \item Weather temperature
\end{itemize}
Methods will be compared by means of the RMSE, MAE and MAPE scores, see section \ref{metrics}.
\subsection{Multiple linear regression}
To get started, standard multiple linear regression has been applied, see figure \ref{fig:mlr_price} for a visualisation. 
\begin{figure}
    \includegraphics[width=\textwidth]{images/mlr_price.png}
    \caption{Multiple linear regression prediction}
    \label{fig:mlr_price}
\end{figure}

@@

% \begin{figure}[!h]
%     \includegraphics[width=\textwidth]{images/prophet_price2.2.png}
%     \caption{Prices trend}
%     \label{fig:prophet_price2.2}
% \end{figure}
Prophet alongside with the right features is a good model in the context of electricity load forecasting, it is capcable of catching the trend, the peak and the lows.

@@

\subsection{Long short term memory}
We used the \href{https://pytorch.org}{torch} library in order to code our LSTM regressor.
Various hyperparameters combinations were tried during the tuning phase. The final architecture we set on follows
\begin{itemize}
    \item hidden\_size= 64
    \item num\_layers= 2
    \item output\_size= 1
    \item num\_epochs= 30
    \item learning\_rate= 0.001
    \item batch\_size= 32
    \item window\_size= 24
\end{itemize}
LSTM forecast is reported in figure \ref{fig:lstm_price}, it achieves a RMSE of 9.1782
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/lstm_price.png}
    \caption{Long short term memory prediction}
    \label{fig:lstm_price}
\end{figure}

\subsection{Kernel ridge regression}
Subsequently, kernel ridge regression was considered. The kernel considered is the radial basis Gaussian function.
Cross validation was carried jointly over the RBF kernel bandwith and the regularization constant.
The RMSE achieved is 9.86, figure \ref{fig:krnridge_price} reports the prediction.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/krnridge_price.png}
    \caption{Kernel ridge prediction}
    \label{fig:krnridge_price}
\end{figure}
We can observe that, kernel ridge regression models accurately the electricity time series.

@@

\subsection{Results}
This section reports the tables comparing the considered methods scores.
% in the context of electricity load forecasting.

@@

The MAE scores are contained in table \ref{tab:point_MAE}. Similarly to above, we can conclude that kernel methods stand out for achieving also the lowest MAE score; with KrnSVR being the top one.
\begin{table}[!ht]
    \caption{Mean absolute errors}
    \label{tab:point_MAE}
    \begin{adjustbox}{width=\textwidth}
        \begin{tabular}{lrrrrrrrrrrrrrrr}
            \toprule
             Method/MAE & Task 1 & Task 2 & Task 3 & Task 4 & Task 5 & Task 6 & Task 7 & Task 8 & Task 9 & Task 10 & Task 11 & Task 12 & Task 13 & Task 14 & Task 15 \\
            \midrule
            MLR & 27.7219 & 24.3823 & 65.4016 & 52.3873 & 34.8465 & 31.2663 & 35.9420 & 34.7316 & 37.0273 & 54.7075 & 48.9327 & 26.1975 & 31.8720 & 29.2306 & 28.3428 \\
            TBATS & 10.5408 & 23.8417 & 91.3153 & 74.5734 & 40.3258 & 26.0092 & 14.2141 & 24.7818 & 62.0452 & 86.7125 & 72.6912 & 28.4235 & 11.1184 & 21.1038 & 31.8555 \\
            Prophet & 8.6139 & 11.4307 & 28.3509 & 46.4480 & 15.6290 & 14.1278 & 10.1574 & 11.2360 & 14.0072 & 18.9565 & 27.1142 & 16.9678 & 14.6615 & 16.1750 & 18.3043 \\
            KNN & 9.4003 & 9.1126 & 19.6213 & 14.4906 & 10.6461 & \textbf{9.4354} & 8.7441 & 10.0065 & 12.4714 & 11.2006 & 20.3087 & 12.5416 & 9.2558 & 8.5937 & 10.5451 \\
            SVR & 20.2443 & 21.2526 & 69.3704 & 57.1107 & 34.3651 & 27.5875 & 27.4651 & 29.4204 & 43.7009 & 64.3522 & 55.4307 & 25.1080 & 24.0294 & 24.4049 & 26.5869 \\
            LSTM & 7.5217 & 9.4767 & \textbf{17.9851} & \textbf{13.2158} & 11.8118 & 9.8607 & \textbf{8.0561} & 10.8480 & 15.1008 & 13.8108 & 25.9906 & 13.3588 & 8.1526 & 9.8000 & 14.3186 \\
            KrnRidge & 7.5965 & 9.2130 & 28.2484 & 24.2366 & \textbf{10.0589} & 10.7758 & 9.5788 & 11.2166 & 12.3427 & 12.3306 & 20.0213 & 10.8434 & 7.1625 & \textbf{7.9710} & 10.0767 \\
            KrnSVR & \textbf{6.9581} & \textbf{8.6989} & 18.7739 & 15.1398 & 10.1395 & 9.5927 & 8.5731 & \textbf{9.0033} & \textbf{11.0618} & \textbf{8.5486} & \textbf{19.7383} & \textbf{10.5545} & \textbf{7.0395} & 8.1926 & \textbf{9.8125} \\
            \bottomrule
            \end{tabular}            
    \end{adjustbox}            
\end{table}

Finally table \ref{tab:point_MAPE} reports the MAPE score for each method. Its results are in line with the other tables, hence suggesting the goodness of kernel methods.
% What can be concluded is that kernel regressors are also the best in terms of MAPE score; with KrnSVR being the top one.
\begin{table}[!ht]
    \caption{Mean absolute percentage errors}
    \label{tab:point_MAPE}
    \begin{adjustbox}{width=\textwidth}
        \begin{tabular}{lrrrrrrrrrrrrrrr}
            \toprule
             Method/MAPE & Task 1 & Task 2 & Task 3 & Task 4 & Task 5 & Task 6 & Task 7 & Task 8 & Task 9 & Task 10 & Task 11 & Task 12 & Task 13 & Task 14 & Task 15 \\
            \midrule
            MLR & 0.2470 & 0.1935 & 0.3030 & 0.2601 & 0.2474 & 0.2667 & 0.3498 & 0.3058 & 0.1954 & 0.2432 & 0.4234 & 0.2114 & 0.2926 & 0.2502 & 0.2145 \\
            TBATS & 0.0833 & 0.1650 & 0.4285 & 0.3731 & 0.2482 & 0.1849 & 0.1234 & 0.1634 & 0.3181 & 0.4021 & 0.4880 & 0.1761 & 0.0905 & 0.1555 & 0.2058 \\
            Prophet & 0.0737 & 0.0854 & 0.1324 & 0.2453 & 0.1134 & 0.1169 & 0.0938 & 0.0912 & 0.0880 & 0.0992 & 0.3757 & 0.1389 & 0.1343 & 0.1356 & 0.1370 \\
            KNN & 0.0778 & 0.0682 & 0.0924 & 0.0761 & 0.0751 & 0.0740 & 0.0784 & 0.0744 & 0.0725 & 0.0555 & \textbf{0.3115} & 0.0888 & 0.0816 & 0.0699 & 0.0765 \\
            SVR & 0.1808 & 0.1640 & 0.3211 & 0.2829 & 0.2317 & 0.2260 & 0.2676 & 0.2451 & 0.2215 & 0.2867 & 0.4354 & 0.1870 & 0.2216 & 0.2044 & 0.1933 \\
            LSTM & 0.0642 & 0.0706 & 0.0896 & \textbf{0.0722} & 0.0798 & 0.0772 & \textbf{0.0710} & 0.0854 & 0.0909 & 0.0741 & 0.3578 & 0.0976 & 0.0719 & 0.0778 & 0.1037 \\
            KrnRidge & 0.0625 & 0.0685 & 0.1281 & 0.1207 & 0.0718 & 0.0797 & 0.0812 & 0.0760 & 0.0696 & 0.0587 & 0.3127 & 0.0779 & \textbf{0.0591} & \textbf{0.0637} & 0.0722 \\
            KrnSVR & \textbf{0.0568} & \textbf{0.0642} & \textbf{0.0892} & 0.0788 & \textbf{0.0714} & \textbf{0.0724} & 0.0740 & \textbf{0.0665} & \textbf{0.0629} & \textbf{0.0428} & 0.3122 & \textbf{0.0781} & 0.0607 & 0.0646 & \textbf{0.0713} \\
            \bottomrule
            \end{tabular}            
    \end{adjustbox}
\end{table}

\section{Probabilistic forecasting}
We continue our experimental analysis by considering the probabilistic framework. The goal of this section is comparing between different quantile regressors and study the choice of the kernel function.

% quantile regressors
\subsection{Quantile regressors comparison}
Using the load data from \href{https://www.energy-charts.info/index.html?l=en&c=DE}{energy charts} for Germany and Switzerland, we proceeded to compare between quantile regression algorithms. In this study, we trained our models on the entire 2021 data and then we tested them and measured their score on the 2022 data.
Notice, for kernel quantile regression (KQR), the kernel of choice in this setting is the absolute Laplacian. Additionally notice, the loss function utilized in this section is the normalized pinball loss. 
% normalized by the magnitude of the average load of each country.
Here, we built two models. In the first, the national load is forecasted by taking as predictor the following variables
\begin{itemize}
    \item Weather temperature
    \item Wind speed
\end{itemize}
Results for Germany are reported in table \ref{tab:energy_chart_de} and figure \ref{fig:DE_load_CI} while results for Switzerland can be found in table \ref{tab:energy_chart_ch} and figure \ref{fig:CH_load_CI}.

@@

    \begin{figure}[!ht]
        \makebox[\linewidth]{\includegraphics[width = 1.5\textwidth]{images/DE_load_CI.png}}
        \caption[Probabilistic forecast for load in Germany]{Load 90\% confidence interval for Germany Energy charts (2022) data using KQR Laplacian. The black line is the observed path for the load. The 90\% confidence interval bands are plotted in green. Lower and upper red lines denote the 95\% and 5\% quantile forecast respectively.}
        \label{fig:DE_load_CI}
    \end{figure}

    \begin{figure}[!ht]
        \makebox[\linewidth]{\includegraphics[width = 1.5\textwidth]{images/CH_load_CI.png}}
        \caption[Probabilistic forecast for load in Switzerland]{Load 90\% confidence interval for Switzerland Energy charts data (2022) using KQR Laplacian. The black line is the observed path for the load. The 90\% confidence interval bands are plotted in green. Lower and upper red lines denote the 95\% and 5\% quantile forecast respectively.}
        \label{fig:CH_load_CI}
    \end{figure}

Next, we extended the models to take into account the impact of two additional categorical variables
\begin{itemize}
    \item Is holiday: a binary variable for holidays, where holiday$=1$ and working day$=0$
    \item Day of week: an ordinal categorical variable corresponding to the day of the week, e.i.\ Monday$=0$,$\dots$, Sunday$=6$
\end{itemize}
Table \ref{tab:energy_chart_de_additional_predictors} reports the model scores on the German data while table \ref{tab:energy_chart_ch_additional_predictors} is the one corresponding to the Suisse data.

\begin{table}[!ht]
    \centering
    \caption{Pinball loss for load in Germany (2022) model\_2}
    \label{tab:energy_chart_de_additional_predictors}
    \begin{tabular}{lrrrr}
    \toprule
    Quantile & LQR & GBMQR & QF & KQR \\
    \midrule
    0.1 & 0.04522 & 0.02580 & 0.02796 & \textbf{0.02491} \\
    0.2 & 0.08048 & 0.04326 & 0.04625 & \textbf{0.04209} \\
    0.3 & 0.10677 & 0.05570 & 0.05706 & \textbf{0.05424} \\
    0.4 & 0.12610 & 0.06182 & 0.06346 & \textbf{0.06071}\\
    0.5 & 0.13767 & 0.06214 & 0.06544 & \textbf{0.06150} \\
    0.6 & 0.14077 & 0.05752 & 0.06001 & \textbf{0.05726} \\
    0.7 & 0.13409 & 0.04893 & 0.05122 & \textbf{0.04869} \\
    0.8 & 0.11628 & 0.03687 & 0.03822 & \textbf{0.03665} \\
    0.9 & 0.08204 & 0.02114 & 0.02324 & \textbf{0.02108} \\
    \midrule
    CRPS & 0.10771 & 0.04591 & 0.04810 & \textbf{0.04524} \\
    \bottomrule
    \end{tabular}
    \end{table}

@@

% now comment tables
What can be concluded from this first study is that kernel quantile regression equipped with the absolute Laplacian kernel outperformed almost always its contenders.

% kernel comparison
\subsection{Kernel function choice}
This section analyzes which kernel function best fits to the characteristics of the load data.
The kernel functions considered are: Gaussian RBF, absolute Laplacian, Matern 1.5, Matern 2.5, Linear, Periodic, Polynomial, Sigmoid, and Cosine. 
Details concerning the hyperparameter selection for the different kernels can be found in \href{https://scikit-learn.org/stable/modules/classes.html#module-sklearn.metrics.pairwise}{sklearn.metrics.pairwise} and \href{https://scikit-learn.org/stable/modules/classes.html#module-sklearn.gaussian_process}{sklearn.gaussian\_process}.
The pool of data for this study has been create by combining \href{https://zenodo.org/records/7907883}{SECURES-Met} data (predictors) \cite{Formayer2023} and the load data from \href{https://www.energy-charts.info/index.html?l=en&c=DE}{energy charts}.
SECURES-Met data consists of historical data up to the end of $2020$ while from 2021 onward, the data consists of forecasts modeled by the the European Centre for Medium-Range Weather Forecasts (ECMWF).
Therefore, in this experimental study, we used the whole data of $2020$ as the training set and then tested our kernels on the $2021$ data.
Note that there are two kinds of predictions for data from $2021$ onward, one for each of the emission scenarios RCP$4.5$ and RCP$8.5$. In this study, we considered the more conservative RCP$4.5$ scenario data.

The predictors making up the datasets follow:
\begin{itemize}
    \item Direct irradiation: direct normal irradiation
    \item Global radiation: mean global radiation
    \item Hydro reservoir: daily mean power from reservoir plants in MW
    \item Hydro river: daily mean power from run of river plants in MW
    \item Temperature: air temperature
    \item Wind potential: potential wind power production
\end{itemize}
Table \ref{tab:secures_met_de} shows results for Germany, table \ref{tab:secures_met_ch} is the one for Switzerland and table \ref{tab:secures_met_at} corresponds to Austria.

@@

\begin{table}[!ht]
    \centering
\caption{Pinball loss kernel comparison for load in Germany (2021)}
\label{tab:secures_met_de}
\begin{adjustbox}{width=\textwidth}
    \begin{tabular}{llllllllll}
\toprule
Quantile & Gaussian RBF & Laplacian & Matern 1.5 & Matern 2.5 & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
\midrule
0.1 & 0.028057 & \textbf{0.027483} & 0.028236 & 0.028257 & 0.028261 & 0.028277 & 0.028276 & 0.028146 & 0.028004 \\
0.2 & 0.047118 & \textbf{0.046051} & 0.047531 & 0.047544 & 0.047569 & 0.047595 & 0.047596 & 0.047353 & 0.047025 \\
0.3 & 0.060366 & \textbf{0.058739} & 0.060892 & 0.060940 & 0.060962 & 0.060988 & 0.060984 & 0.060654 & 0.060209 \\
0.4 & 0.068344 & \textbf{0.066347} & 0.068952 & 0.069022 & 0.069054 & 0.069104 & 0.069101 & 0.068634 & 0.068202 \\
0.5 & 0.071450 & \textbf{0.069118} & 0.072188 & 0.072250 & 0.072285 & 0.072331 & 0.072330 & 0.071807 & 0.071359 \\
0.6 & 0.068821 & \textbf{0.067098} & 0.069454 & 0.069526 & 0.069571 & 0.069615 & 0.069613 & 0.069157 & 0.068780 \\
0.7 & 0.061150 & \textbf{0.059972} & 0.061382 & 0.061410 & 0.061427 & 0.061442 & 0.061442 & 0.061281 & 0.060990 \\
0.8 & 0.047147 & \textbf{0.046457} & 0.047325 & 0.047331 & 0.047340 & 0.047348 & 0.047349 & 0.047247 & 0.047056 \\
0.9 & 0.026646 & 0.026343 & 0.026749 & 0.026757 & 0.026763 & 0.026772 & 0.026772 & \textbf{0.026282} & 0.026628 \\ 
\midrule
CRPS & 0.053233 & \textbf{0.051956} & 0.053634 & 0.053671 & 0.053693 & 0.053719 & 0.053718 & 0.053395 & 0.053139 \\
\bottomrule
\end{tabular}
\end{adjustbox}
\end{table}

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\linewidth]{images/price_task_6_gaussian_rbf.png}
    \caption[Prediction price track task 6, Gaussian RBF kernel]{Price 90\% confidence interval task 6. Electricity price probabilistic forecast for the $13^{\text{th}}$ July $2013$. The black line is the observed path for the price. The $90\%$ confidence interval bands are plotted in green. Lower and upper red lines denote the $95\%$ and $5\%$ quantile forecast respectively.}
    % \Description{}
    \label{fig:price_task_6_gaussian_rbf}
\end{figure}
